Staged Abstract Interpreters

### 2019-09-11 paper/70_eval.tex
polish

\section{Empirical Evaluation} \label{evaluation}

@@

\vspace{-5pt}
\paragraph{Implementation and Evaluation Environment} We implement the abstract
interpreters for control-flow analysis, i.e., a value-flow analysis that
computes which lambda terms can be called at each call-site.
With other suitable abstract domains, the abstract interpreter
can also be extended to other analyses.
A front-end desugars Scheme to a small core language that makes the analyzer
easy to implement. We implement two common monovariant 0-CFA-like analyses: one
is equipped with store-widening (0CFA-SW for short), the other is not (0CFA
for short). It is traditionally expected that the store-widened analysis be faster than the
alternative.  Our prototype implementation currently generates Scala code; the
generated Scala code will be compiled and executed on the JVM, though it is possible to
generate C/C++ code in the future. In the experiments, we implement several
optimizations mentioned in Section \ref{staged_ds}, specifically, the selective
caching scheme and IR-level rewriting rules (for pairs, lists, sets, and maps)
that exploit partially-static data. These optimizations are useful to reduce
the size of generated code.

We use Scala 2.12.8 and Oracle JVM 1.8.0-191 \footnote{The options for
running the JVM are set to the following: \texttt{-Xms2G -Xmx8G -Xss1024M
-XX:MaxMetaspaceSize=2G - XX:ReservedCodeCacheSize=2048M}},
running on an Ubuntu 16.04 LTS (kernel 4.4.0) machine. All of our
evaluations were performed on a machine with 4 Intel Xeon Platinum
8168 CPU at 2.7GHz and 3 TB of RAM. Although the machine has 96 cores
(192 threads) in total, the abstract interpreters are single-threaded.
To minimize the effect of warm-up from the HotSpot JIT compiler,
all the experiments are executed for 20 times and we report the
statistical median value of the running times. We set a 5 minute
timeout.

>>>>

\section{Performance Evaluation} \label{evaluation}

@@

\vspace{-5pt}
\paragraph{Implementation and Evaluation Environment} We implement the abstract
interpreters for control-flow analysis, i.e., a value-flow analysis that
computes which lambda terms can be called at each call-site.
With other suitable abstract domains, the abstract interpreter
can also be extended to other analyses.
A front-end desugars Scheme to a small core language that makes the analyzer
easy to implement. We implement two common monovariant 0-CFA-like analyses: one
is equipped with store-widening (0CFA-SW for short), the other one is not (0CFA
for short). It is traditionally expected that the store-widened analysis be faster than the
alternative.  Our prototype implementation currently generates Scala code. The
generated Scala code will be compiled and executed on the JVM, though it is possible to
generate C/C++ code in the future. In the experiments, we implement several
optimizations mentioned in Section \ref{staged_ds}, specifically, including the
selective caching scheme and IR-level rewriting rules (for pairs, lists, sets,
and maps) that exploit partially-static data. These optimizations are useful to
reduce the size of generated code and improve performance.

We use Scala 2.12.8 and Oracle JVM 1.8.0-191 \footnote{The options for
running the JVM are set to the following: \texttt{-Xms2G -Xmx8G -Xss1024M
-XX:MaxMetaspaceSize=2G - XX:ReservedCodeCacheSize=2048M}},
running on an Ubuntu 16.04 LTS (kernel 4.4.0) machine. All our
evaluations were performed on a machine with 4 Intel Xeon Platinum
8168 CPU at 2.7GHz and 3 TB of RAM. Although the machine has 96 cores
(192 threads) in total, the abstract interpreters are single-threaded.
To minimize the effect of warm-up from the HotSpot JIT compiler,
all the experiments are executed for 20 times and we report the
statistical median value of the running times. We set a 5 minute
timeout.
